Smart Spreading Factor Assignment for LoRaWANs

### 2018-12-31 paper.tex
interference

@@

@@

\section{Conclusion} \label{Conclusion}
\par In this paper, after brief introduction about LPWAN technologies, we provide background information about one of the most promising LPWAN technology, LoRa. Then, we discuss about LoRa modulation basics and spreading factor assignment issue. We have implemented a discrete event simulator from scratch to study network performance of LoRaWAN and evaluate different SF assignment schemes. We have shown how same SF transmission collisions can be avoided and we proposed a machine learning based solution for collision with same SF transmissions. We illustrate simulation results for proposed machine learning SF assignment technique. Our simulation results show that, proposed technique can increase network performance up to [TODO] \%.

>>>>

\begin{equation} \label{eq:sinr_db}
SINR_{i,j} = \dfrac{P_{rc,0}}{\sum_{l \in I_j} P_{rc,l}}
\end{equation}

\begin{equation} \label{eq:sinr_t}
SINR_{i,j}^{dB} > T_{i,j}
\end{equation}

\begin{equation} \label{eq:p_interference}
P_{rc,y}^{interf} = \dfrac{P_{rc,y}(T_{x}-t_{1})}{T_{x}}
\end{equation}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{predict_pdr}
\caption{PDR of different prediction SF assignment scheme.}
\label{fig:pr_pdr}
\end{figure}

@@

\section{Conclusion} \label{Conclusion}
\par In this paper, after brief introduction about LPWAN technologies, we provide background information about one of the most promising LPWAN technology, LoRa. Then, we discuss about LoRa modulation basics and spreading factor assignment issue. We have implemented a discrete event simulator from scratch to study network performance of LoRaWAN and evaluate different SF assignment schemes. We have shown how same SF transmission collisions can be avoided and we proposed a machine learning based solution for collision with same SF transmissions. We illustrate simulation results for proposed machine learning SF assignment technique. Our simulation results show that, proposed technique can increase network performance up to [TBD] \%.
